\documentclass[requirements.tex]{subfiles}
\begin{document}
\section{Market Analysis} % (fold)
\label{sec:market_analysis}

There are some examples in the market of different approaches to text input
using game controllers, although they are only on two different platforms:
Sony's Playstation 4 console and Valve's Steam platform on PC.

\subsection{Dualshock 4 Gyroscopic} % (fold)
\label{sub:dualshock_4_gyroscopic}
The Playstation 4's Dualshock 4 controller has gyroscopic technology included,
which allows for a input method utilising it. The keyboard still has the single
character selection of the traditional method, but now its movement is
controlled by the movement of the physical controller rather than button presses
or analogue stick movement. This does result in faster movement from one side of
the keyboard to another, although there is the draw back of this being a much
more physical activity which can become tedious on longer usage. Another method
of manipulating the cursor during text input is using the controller's touch pad
instead of using the directional pad or analogue stick, although this method
does not feel different to the user in practise in comparison, making it not as
interesting as an example.
% subsection dualshock_4_gyroscopic (end)

\subsection{Steam Controller} % (fold)
\label{sub:steam_controller}
Valve's offerings in this subject are are more interesting, with it being clear
that this is a challenge that they have approached with much consideration.

The first solution is based on their own controller, the Steam Controller, which
is a games controller that provides two trackpads and one analogue stick, rather
than sticking to the traditional controller layout of two analogue sticks and
direction pad. This means that they had an opportunity to provide a new way of
text input. The two trackpads can be used to control two separate cursors
instead of just the one, with shoulder buttons being used to enter characters.
This method offers the advantage of it being much quicker to enter character
sequences such as `qu', which is appreciated. However, since the user is doing
the same task twice with each hand, there is another learning curve obstacle
since some users may find it difficult to move both cursors at the same time.
% subsection steam_controller (end)

\subsection{Steam Big Picture Mode} % (fold)
\label{sub:steam_big_picture_mode}
The second such solution is found in their `Big Picture' mode, which provides an
interface designed for being use at a longer distance between user and display.
The keyboard is divided into 8 groups of 4 characters, arranged in a circle.
The left analogue stick chooses between each of these groups, depending on the
position of the stick. The face buttons (A, B, X, Y on XBox or Cross, Circle,
Square, Triangle on Playstation) are then used to choose the specific character.

Out of the three solutions found in market, it is this approach from Valve that
I find the most interesting, due to it's ability to tackle the goal of allowing
more character access at once. However, I feel that the arrangement demanded by
this input method is too different from the traditional method, which results
in a learning curve that I feel is too large for the task at hand. My design for
text input is an attempt to take the mindset shown by Valve, but applied to
take advantage of the traditional keyboard layout.
% subsection steam_big_picture_mode (end)
% section market_analysis (end)
\newpage
\end{document}